Remark on the hypothetical judgment

### 2015-08-01 paper.tex
typo

In addition to the categorical judgments above, higher-order forms of judgment
are also explained, including the hypothetical judgment and the general
judgment. Now, the primitive hypothetical judgment
$\HypJ{\JJ_2}{\JJ_1}$,\footnote{Hypothetical judgment is to be distinguished
from the sequent judgments $\Seq{\Gamma}{\cdots}$, which is not a higher-order
judgment at all.} was explained by Martin-L\"of in terms of his definition of a
hypothetical \emph{proof} or \emph{demonstration}, which is as follows:

>>>>

In addition to the categorical judgments above, higher-order forms of judgment
are also explained, including the hypothetical judgment and the general
judgment. Now, the primitive hypothetical judgment
$\HypJ{\JJ_2}{\JJ_1}$,\footnote{Hypothetical judgment is to be distinguished
from the sequent judgments $\Seq{\Gamma}{\cdots}$, which are not even
higher-order judgments at all.} was explained by Martin-L\"of in terms of his
definition of a hypothetical \emph{proof} or \emph{demonstration}, which is as
follows:
